Template Master's Thesis

### 2023-08-17 paper.tex
Update paper

413 addresses, 161 clusters, most clusters of 2 or 3 addresses, one cluster of 71 addresses.
From the remaining 413 addresses, we can form 161 clusters. Most clusters consists of 2 or 3 addresses. There is one cluster of 71 addresses which is likely

>>>>

From the remaining 413 addresses, we can form 161 clusters. The clusters are visualized in Figure \ref{fig:LAND_clusters}. Most clusters consist of 2 or 3 addresses, one cluster of 71 addresses. Marked in green.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.6\textwidth]{../figures/land_clusters.png}
	\caption{LAND clusters}
	\label{fig:LAND_clusters}
\end{figure}

This cluster is also observable when we visualize the LAND token network.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.6\textwidth]{../figures/land_network.png}
	\caption{LAND token network, edges blue indicate a purchase}
	\label{fig:LAND_network}
\end{figure}
